---
title: "Comprehensive statistics on the 2014 election in Sweden"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab05)
```

# Function in this Package
<p> This package is to represent the election results of Sweden in the year 2014. This package has two functions. The source is received with a url.

<p> CountyResults is to represent the votes for each party in each county. It takes argument, county_name as character and return the bar plot for the votes for each party.

<p> MunicipalityResults is to represent the votes for each party in each municipality. It takes the argument, municipality_name as character and return the bar plot for the votes for each party.

<p> The functions are defined in a separate R file and passed into shiny app. This way it will makes the process easy. An example for both the functions are shown below.
```{r example,eval=TRUE,fig.width = 14, fig.height = 9, out.width = "588", out.height = "378"}
Municipality(MunicipalityInput = "Dalarnas län")
PercentageCalc(PercentageInput = "Dalarnas län")
```
```{r run, eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# run the shiny app from github
shiny::runGitHub('Lab05', 'menon1234')
```

